---
title: "Finding RSEs and Data scientists"
output: html_notebook
---

This notebook uses tweetR to find RSEs (and RSE-like people) using twitter data.

```{r setup}

library(rtweet)
library(tidyverse)
library(wordcloud)

account <- "ResearchSoftEng"
maxFriends <- 250
```




We use the `r account` account as a seed; this is the official Twitter account of the RSE association.  We assume that everyone following this is an RSE.

```{r}

rse_follows <- get_followers(account)
rse_follows_data <- lookup_users(rse_follows$user_id)
```

There are two approaches we can use:

1. Look at how RSEs describe themselves, and look for similar terms in other users' descriptions
2. Look at accounts that RSEs follow, and then look for other accounts that also follow these accounts

Looking at the description data:
```{r}
descriptionMinusCommon <- str_replace(tolower(rse_follows_data$description), "research", "")
suppressWarnings(wordcloud(descriptionMinusCommon))
```




Looking at the second approach:   In order to avoid getting excessively hit by the Twitter API's rate limit, we'll *only* look at people following fewer than `r maxFriends`.  This isn't ideal, and will likely bias our results:

```{r}
rse_follows_data <- lookup_users(rse_follows$user_id)

summary(rse_follows_data$friends_count)
```

```{r}
followsfollows <- rse_follows_data %>% 
  filter(friends_count <= maxFriends) # %>% 
   mutate(rownum = row_number()) %>% 
   filter(rownum <= 15) 

friends <- get_friends(followsfollows$user_id, retryonratelimit = TRUE)

friends %>% group_by(user) %>% 
  summarise(numincommon = sum(user_id %in% rse_follows_data$user_id))
  
```

